TBD

### 2021-02-26 outputs/paper/paper.Rmd
Add install package for 'gridExtra'

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(bookdown)
library(tidyverse)
library(ggplot2)
library(kableExtra)
library(janitor)
library(dplyr)
library(ggthemes)
library(broom)
library(purrr)
library(gridExtra)
#devtools::install_github("johannesbjork/LaCroixColoR")
library(LaCroixColoR)
all_simulated_dataset <- 
  readr::read_csv("../../inputs/data/simulated_data.csv")

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(bookdown)
library(tidyverse)
library(ggplot2)
library(kableExtra)
library(janitor)
library(dplyr)
library(ggthemes)
library(broom)
library(purrr)
# install.packages('gridExtra')
library(gridExtra)
#devtools::install_github("johannesbjork/LaCroixColoR")
library(LaCroixColoR)
all_simulated_dataset <- 
  readr::read_csv("../../inputs/data/simulated_data.csv")
